Reasoning about Connectors in Coq

### 2017-05-28 FACS_Extension/paper_revised0508.tex
update lstlistings configuration

\usepackage[normalem]{ulem}
\usepackage{todonotes}
\usepackage{color}
\usepackage{verbatim}
\newcommand{\redt}[1]{\textcolor{red}{#1}}
\newcommand{\liyi}[1]{\textcolor{blue}{#1}}
%\newcommand{\xyz}[1]{\textcolor{blue}{#1}}

@@

@@

Coq\cite{huet1997coq} is a widely-used proof assistant tool, where denotational formalizations (e.g.
theorem and hypothesis) and operational formalizations (e.g. functions and algorithms) are naturally
integrated. Moreover, it allows the interactive construction of formal proofs.
The formal language used in Coq is called \emph{Gallina}, which provides a convenient way to define
both programming statements and mathematical propositions, for example:
\begin{verbatim}
  (* a variable definition *)
  Variables a b: nat.
  (* a simple non-recursive function *)
  Definition inc(a:nat) := a + 1.
  (* axioms don't have to be proved *)
  Axiom inc_ax: forall c:nat, inc(c) > c.
  (* theorems rely on proving *)
  Theorem inc_eq: forall c:nat, inc(c) = c + 1.
  Proof.
    (* interactive proving based on tactics *)
    auto.
  Qed.
\end{verbatim}

@@

The merge operator is more complicated. We consider merging two
channels \emph{AB} and \emph{CD}. When the merge operator acts on
these two channels, it leads to a choice of taking from the common
node that delivers a data item out of \emph{AB} or \emph{CD}.
%If both channels have data items available, the choice is
%non-deterministic\footnote{Choices are made by external context, so
%the definition here remains deterministic.}.
Similar to the definition of basic channels, we define merge as the intersection of two predicates and use recursive definition here:
%    Definition xor(a b: Prop) :=  (a \/ b) /\ ~(a /\ b).
\begin{verbatim}
    Parameter merge:
    Stream TD -> Stream TD ->Stream TD -> Prop.
    Axiom merge_coind:
      forall s1 s2 s3:Stream TD,
      merge s1 s2 s3-> (
        ~ (PrL(hd s1) = PrL(hd s2)) /\
        (
          (PrL(hd s1) < PrL(hd s2)) ->
          ((hd s3 = hd s1)  /\ merge (tl s1) s2 (tl s3))
        ) /\ (
          (PrL(hd s1) > PrL(hd s2)) ->
          ((hd s3 = hd s2)  /\ merge s1 (tl s2) (tl s3))
        )
      ).
\end{verbatim}

>>>>

\usepackage[normalem]{ulem}
\usepackage{todonotes}
\usepackage{color}
\usepackage{verbatim}
\usepackage{listings}

\newcommand{\redt}[1]{\textcolor{red}{#1}}
\newcommand{\liyi}[1]{\textcolor{blue}{#1}}
%\newcommand{\xyz}[1]{\textcolor{blue}{#1}}

@@

\lstset{
    basicstyle=\ttfamily, 
    numbers=left,
    numberstyle=\small,
    columns=flexible,
    numbersep=10pt,
    tabsize=2,
    extendedchars=true,         %
    breaklines=true,
    keywordstyle=\bfseries,
    stringstyle=\color{white}\ttfamily, % Farbe der String
    xleftmargin=20pt,
    framexleftmargin=17pt,
    framexrightmargin=5pt,
    framexbottommargin=4pt,
    showstringspaces=false,
    frame=single
}

\lstdefinelanguage{coq}{
    keywords = {
        Parameter, Parameters, Variable, Variables,
        Fixpoint,
        Stream, Prop,
        forall, exists,
        Axiom, Lemma, Goal, Theorem,
        Proof, Qed
    }
}

\renewcommand{\ttdefault}{pxtt}

@@

Coq\cite{huet1997coq} is a widely-used proof assistant tool, where denotational formalizations (e.g.
theorem and hypothesis) and operational formalizations (e.g. functions and algorithms) are naturally
integrated. Moreover, it allows the interactive construction of formal proofs.
The formal language used in Coq is called \emph{Gallina}, which provides a convenient way to define
both programming statements and mathematical propositions, for example:
\begin{lstlisting}[language=coq]
  (* a variable definition *)
  Variables a b: nat.
  (* a simple non-recursive function *)
  Definition inc(a:nat) := a + 1.
  (* axioms don't have to be proved *)
  Axiom inc_ax: forall c:nat, inc(c) > c.
  (* theorems rely on proving *)
  Theorem inc_eq: forall c:nat, inc(c) = c + 1.
  Proof.
    (* interactive proving based on tactics *)
    auto.
  Qed.
\end{lstlisting}

@@

The merge operator is more complicated. We consider merging two
channels \emph{AB} and \emph{CD}. When the merge operator acts on
these two channels, it leads to a choice of taking from the common
node that delivers a data item out of \emph{AB} or \emph{CD}.
%If both channels have data items available, the choice is
%non-deterministic\footnote{Choices are made by external context, so
%the definition here remains deterministic.}.
Similar to the definition of basic channels, we define merge as the intersection of two predicates and use recursive definition here:
%    Definition xor(a b: Prop) :=  (a \/ b) /\ ~(a /\ b).
\begin{lstlisting}
    Parameter merge:
    Stream TD -> Stream TD ->Stream TD -> Prop.
    Axiom merge_coind:
      forall s1 s2 s3:Stream TD,
      merge s1 s2 s3-> (
        ~ (PrL(hd s1) = PrL(hd s2)) /\
        (
          (PrL(hd s1) < PrL(hd s2)) ->
          ((hd s3 = hd s1)  /\ merge (tl s1) s2 (tl s3))
        ) /\ (
          (PrL(hd s1) > PrL(hd s2)) ->
          ((hd s3 = hd s2)  /\ merge s1 (tl s2) (tl s3))
        )
      ).
\end{lstlisting}
